---
title: "Tutorial 4 week5"
format: html
bibliography: references.bib
---


```{r}
#| label: fig-penguins-scatter
#| fig-cap: "Body mass vs. Flipper length for three penguin species."
#| warning: false
library(ggplot2)
library(palmerpenguins)

ggplot(penguins, aes(x = flipper_length_mm, y = body_mass_g, color = species)) +
  geom_point() +
  theme_minimal()
```

@fig-penguins-scatter illustrates the relationship between flipper lenght and body mass between different pengiun species.


```{r}
#| label: tbl-penguin-summary
#| tbl-cap: "Mean body mass of penguins by species and sex."
#| warning: false
#| echo: false
library(dplyr)

penguins |>
  filter(!is.na(sex)) |>
  group_by(species, sex) |>
  summarise(mean_mass = mean(body_mass_g)) |>
  knitr::kable()
```

@tbl-penguin-summary summarises the average body mass of penguins by sex and species. 
Try to avoid using space in table or figure name. Use '@' follows by figure/table names to reference them.

## Reference
This dataset is sourced from [@penguin_data]

This dataset is sourced from @penguin_data

It works with or without '[]' but without the '[]' the name of the author will not be within a '()'. can be used like below;

@penguin_data argued that penguins xxx.